{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-18 paper/paper.tex
explained rule for `store`

>>>>

The security levels in $LType$ are the security levels of the operands in the local state. To
express our security policy, we declare a function $\Gamma(x)$ that assigns to every variable
$x$ a security level. If we now want to \texttt{store} the top of the stack into the variable
$x$ one premise is that the security level of the program point ($se(i)$) \textit{and} the
security level of the value on top of the operand stack is \textit{lower or equal} to the
security level that was assigned by $Gamma$ to the variable $x$. If this is the case the head
of $LType$ is removed.
